Self Regulation Ontology Retest Analyses

### 2018-10-15 code/SRO_Retest_Analyses.Rmd
refactoring

```{r}
#summary(lmerTest::lmer(abs(difference) ~ scale(days_btw)+(scale(days_btw) | dv), data=t1_2_difference))

summary(tmp <- MCMCglmm(abs(difference) ~ scale(days_btw), random = ~us(scale(days_btw)):dv, data=t1_2_difference, verbose=FALSE))
```

@@

# tmp = duplicate_items %>%
#   select(similarity, t1_t1_polycor, t1_t2_polycor, t2_t2_polycor, t2_t1_polycor) %>%
#   gather(key, value, -similarity)

tmp %>%
  ggplot(aes(similarity, value, col=key))+
  geom_smooth(method="lm", alpha = 0.15)+
  ylab("Polychoric correlation")+
  xlab("Levenshtein distance")+
  scale_color_discrete(breaks = c("t1_t1_polycor", "t2_t2_polycor"),
                       labels = c("T1 correlations", "T2 correlations"),
                       name = element_blank())+
  theme_bw()

ggsave('OverlappingItemSimilarity.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 500)
```

@@

```{r}
summary(MCMCglmm(value ~ key*scale(similarity), data=tmp, nitt = 50000))
```

Time 1: item 1 - item 2
Time 1 item 1 - time 2 item 2
Time 2 item 1 - time 1 item 2
Time 2: item 1 - item 2

```{r warning=FALSE, message=FALSE}
tmp = duplicate_items_data_t1 %>%
  gather(key, value, -worker)

tmp2 = duplicate_items_data_t2 %>%
  gather(key, value, -worker)

tmp = duplicate_items %>%
  select(item1_ID, item2_ID) %>%
  left_join(tmp, by = c("item1_ID" = "key")) %>%
  left_join(tmp, by = c("item2_ID" = "key", "worker" = "worker")) %>%
  rename(item1_time1 = value.x, item2_time1 = value.y) %>%
  left_join(tmp2, by = c("item1_ID" = "key", "worker" = "worker")) %>%
  left_join(tmp2, by = c("item2_ID" = "key", "worker" = "worker")) %>%
  rename(item1_time2 = value.x, item2_time2 = value.y) %>%
  group_by(item1_ID) %>%
  mutate(item1_time1 = scale(item1_time1),
         item1_time2 = scale(item1_time2),
         item2_time1 = scale(item2_time1),
         item2_time2 = scale(item2_time2),
         item1_time1 = ifelse(item1_ID == "mpq_control_survey.13", item1_time1*-1, item1_time1),
         item1_time2 = ifelse(item1_ID == "mpq_control_survey.13", item1_time2*-1, item1_time2)) %>%
  ungroup()

p1 = tmp %>%
  ggplot(aes(item1_time1, item2_time1, col=item1_ID))+
  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
  theme(legend.position = "none")+
  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
  xlab("Item 1 T1")+
  ylab("Item 2 T1")

p2 = tmp %>%
  ggplot(aes(item1_time1, item2_time2, col=item1_ID))+
  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
  theme(legend.position = "none")+
  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
  xlab("Item 1 T1")+
  ylab("Item 2 T2")

p3 = tmp %>%
  ggplot(aes(item1_time2, item2_time1, col=item1_ID))+
  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
  theme(legend.position = "none")+
  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
  xlab("Item 1 T2")+
  ylab("Item 2 T1")

p4 = tmp %>%
  ggplot(aes(item1_time2, item2_time2, col=item1_ID))+
  geom_smooth (alpha=0.3, size=0, span=0.5, method = "lm")+
  stat_smooth (geom="line", alpha=1, size=1, span=0.5, method= "lm")+
  theme(legend.position = "none")+
  geom_abline(slope=1, intercept=0, size = 2, linetype = "dashed")+
  xlab("Item 1 T2")+
  ylab("Item 2 T2")

p5 = arrangeGrob(p1, p2, p3, p4, ncol=2)

ggsave('DataCheckOverlappingItems.jpg', p5, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 8, height = 5, units = "in", limitsize = FALSE, dpi = 500)

rm(tmp, tmp2, p1, p2, p3, p4, p5)
```

@@

Distribution of reliabilities, sample sizes and delays

@@

rel_comp %>%
  group_by(task) %>%
  summarise(mean_sample_size = mean(sample_size),
            sem_sample_size = sem(sample_size)) %>%
  ggplot(aes(task,mean_sample_size,col=task))+
  geom_point(size=5)+
  geom_errorbar(aes(ymin=mean_sample_size-sem_sample_size, ymax=mean_sample_size+sem_sample_size), width = 0, size=2)+
  xlab("")+
  ylab("Sample size")+
  theme(legend.position = 'none',
        axis.text.x = element_text(size=14),
        axis.title.y = element_text(size=14))

ggsave('LitReviewSampleSize.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 3, height = 5, units = "in", limitsize = FALSE, dpi = 500)
```

@@

```{r}
# summary(lm(sample_size ~ task,rel_comp))
summary(m1 <- MCMCglmm(sample_size ~ task, data=rel_comp))
```

@@

```{r}
#summary(mod2)
summary(MCMCglmm(retest_reliability ~ task + sample_size, random = ~ dv, data = rel_comp))
```

@@

```{r}
rel_comp %>%
  ggplot(aes(sample_size, retest_reliability, color=task))+
  geom_smooth(method='lm')+
  # geom_point(alpha = 0.2)+
  theme(legend.title = element_blank(),
        axis.title.y = element_text(size=14),
        axis.title.x = element_text(size=14))+
  xlab("Sample Size")+
  ylab("Retest reliability")+
  ylim(-0.15, 1)

ggsave('LitReviewRelBySampleSize.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 8, height = 5, units = "in", limitsize = FALSE, dpi = 500)
```

@@

```{r}
rel_comp %>%
  ggplot(aes(task, retest_reliability, fill = task))+
  geom_boxplot()+
  theme(legend.position = 'none',
        axis.text.x = element_text(size=14),
        axis.title.y = element_text(size=14))+
  xlab("")+
  ylab("Mean ICC")+
  ylim(-0.4,1)

ggsave('LitTaskVsSurvey.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 3, height = 5, units = "in", limitsize = FALSE, dpi = 500)
```

@@

```{r}
n_df = rel_comp %>%
  group_by(dv) %>%
  tally()

@@

#lit_emp_cor_out = plyr::rdply(100, lit_emp_cor)

#write.csv(lit_emp_cor_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/lit_emp_cor_out.csv')

lit_emp_cor_out = read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/lit_emp_cor_out.csv')

summary(lit_emp_cor_out)

@@

```{r}
comp_lit_pred <- function(df){

@@

comp_lit_pred_out = plyr::rdply(1000, comp_lit_pred(rel_comp))
```

```{r}
tmp = comp_lit_pred_out %>%
  select(-.n, -m_lit, -m_boot) %>%
  gather(key, value) %>%
  separate(key, c("stat", "sample"), sep = "_")

# tmp$stat = as.factor(tmp$stat)
# levels(tmp$stat) <- c("coefficient", expression(r^"2"))

tmp %>%  
  ggplot(aes(value, fill=sample))+
  geom_density(alpha = 0.5, position='identity', color=NA)+
  # facet_grid(.~stat, scales='free', labeller = label_parsed)+
  scale_fill_manual(breaks=c("boot","lit"),
                       labels=c("Empirical", "Literature"),
                      name="Predictor",
                      values = c("gray15", "gray75"))+
  xlab('Proportion of Variance in Literature Explained')+
  ylab('Density')+
  xlim(0,1)+
  ylim(0,40)+
  theme(#axis.title.x  = element_text(size=12),
        #axis.text.x  = element_text(size=12),
        #axis.text.y  = element_text(size=12),
        #axis.title.y  = element_text(size=12),
        #legend.title  = element_text(size=12),
        #legend.text  = element_text(size=12),
        legend.position = "bottom",
        plot.caption = element_text(family = "Times", lineheight = 2, hjust = 0))+
  labs(caption = str_wrap("FIGURE 3: Noise ceiling for comparing empirical retest reliability estimates to reliability estimates from the literature. Data come from sampling a single reliability estimate from the literature and using that as a predictor of the remaining retest reliability estimates from the literature versus using the mean estimate from our empirical results as a predictor. Models account for the effect of sample size in the literature and whether the measure is a task or survey variables. The literature samples are significantly better at predicting the rest of the literature than our empirical averages, but the distributions of variance explained across samples are highly overlapping. ", width = 120))

ggsave('LitAndBoot_Noise_Ceiling.tiff', device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 7, height = 5, units = "in", limitsize = FALSE, dpi = 300)
```

>>>>

```{r}
summary(lmerTest::lmer(abs(difference) ~ scale(days_btw)+(scale(days_btw) | dv), data=t1_2_difference))

# summary(tmp <- MCMCglmm(abs(difference) ~ scale(days_btw), random = ~us(scale(days_btw)):dv, data=t1_2_difference, verbose=FALSE))
```

@@

tmp %>%
  ggplot(aes(similarity, value, col=key))+
  geom_smooth(method="lm", alpha = 0.15)+
  ylab("Polychoric correlation")+
  xlab("Levenshtein distance")+
  scale_color_discrete(breaks = c("t1_t1_polycor", "t2_t2_polycor"),
                       labels = c("T1 correlations", "T2 correlations"),
                       name = element_blank())+
  theme_bw()
```

@@

```{r eval=FALSE, echo=FALSE}
summary(MCMCglmm(value ~ key*scale(similarity), data=tmp, nitt = 50000))
```

@@

Distribution of reliabilities, sample sizes and delays in the literature

@@

rel_comp %>%
  group_by(task) %>%
  summarise(mean_sample_size = mean(sample_size),
            sem_sample_size = sem(sample_size)) %>%
  ggplot(aes(task,mean_sample_size,col=task))+
  geom_point(size=5)+
  geom_errorbar(aes(ymin=mean_sample_size-sem_sample_size, ymax=mean_sample_size+sem_sample_size), width = 0, size=2)+
  xlab("")+
  ylab("Sample size")+
  theme(legend.position = 'none',
        axis.text.x = element_text(size=14),
        axis.title.y = element_text(size=14))
```

@@

```{r}
# summary(lm(sample_size ~ task,rel_comp))
summary(m1 <- MCMCglmm(sample_size ~ task, data=rel_comp, verbose=FALSE))
```

@@

```{r}
#summary(mod2)
summary(MCMCglmm(retest_reliability ~ task + sample_size, random = ~ dv, data = rel_comp, verbose=FALSE))
```

@@

```{r}
rel_comp %>%
  ggplot(aes(sample_size, retest_reliability, color=task))+
  geom_smooth(method='lm')+
  # geom_point(alpha = 0.2)+
  theme(legend.title = element_blank(),
        axis.title.y = element_text(size=14),
        axis.title.x = element_text(size=14))+
  xlab("Sample Size")+
  ylab("Retest reliability")+
  ylim(-0.15, 1)
```

@@

```{r}
rel_comp %>%
  ggplot(aes(task, retest_reliability, fill = task))+
  geom_boxplot()+
  theme(legend.position = 'none',
        axis.text.x = element_text(size=14),
        axis.title.y = element_text(size=14))+
  xlab("")+
  ylab("Mean ICC")+
  ylim(-0.4,1)
```

@@

```{r eval=FALSE}
n_df = rel_comp %>%
  group_by(dv) %>%
  tally()

@@

lit_emp_cor_out = plyr::rdply(100, lit_emp_cor)

write.csv(lit_emp_cor_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/lit_emp_cor_out.csv')
```

```{r echo=FALSE}
lit_emp_cor_out = read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/lit_emp_cor_out.csv')

summary(lit_emp_cor_out)
```

@@

```{r eval=FALSE}
comp_lit_pred <- function(df){

@@

comp_lit_pred_out = plyr::rdply(1000, comp_lit_pred(rel_comp))

write.csv(comp_lit_pred_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/comp_lit_pred_out.csv')
```

```{r echo=FALSE}
comp_lit_pred_out = read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/comp_lit_pred_out.csv')
```

```{r echo=FALSE, out.width='100%'}
fig_name = 'LitAndBoot_Noise_Ceiling.jpeg'
